SAT Competition 2020\tnoteref{title}

### 2020-12-16 paper/main.tex
more on the selected benchmarks

@@

\todo{}

@@

\section{Analysis of Results}
\label{sec:analysis}

In the following we provide a summary of the new strategies implemented in the award winning solvers in this competition.

\subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}

In the main track, a total of $18$ teams submitted their solvers to the competition.  
Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
$11$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or Cadical~\cite{}.

In the incremental track, four teams submitted their solvers. 
Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers.

@@

\subsection{Parallel SAT Solving: Winners of the Parallel Track}

@@

\subsection{Massively Parallel SAT Solving: Winners of the Cloud Track}

>>>>

Table~\ref{tab:families} displays the numbers of submitted, interesting and finally selected instances grouped by problem family.

\begin{table}[h]
\centering
\begin{tabular}{rrr||l}
submitted & interesting & selected & family\\
\hline\hline
6 & 2 & 2 & 01-integer-programming\\
187 & 139 & 14 & antibandwidth\\
40 & 20 & 13 & baseball-lineup\\
393 & 333 & 14 & bitvector\\
20 & 15 & 12 & cellular-automata\\
38 & 18 & 7 & cnf-miter\\
14 & 14 & 14 & coloring\\
20 & 20 & 14 & core-based-generator\\
18 & 13 & 13 & cover\\
106 & 93 & 34 & cryptography\\
20 & 19 & 7 & discrete-logarithm\\
58 & 57 & 7 & edge-matching\\
8 & 5 & 5 & fermat\\
40 & 3 & 0 & flood-it-puzzle\\
20 & 19 & 13 & hgen\\
56 & 48 & 14 & hypertree-decomposition\\
20 & 16 & 14 & influence-maximization\\
20 & 20 & 9 & lam-discrete-geometry\\
20 & 20 & 8 & polynomial-multiplication\\
4 & 2 & 2 & schur-coloring\\
20 & 20 & 12 & station-repacking\\
23 & 19 & 7 & stedman-triples\\
5 & 2 & 2 & sum-subset\\
20 & 20 & 14 & tensors\\
12 & 7 & 7 & termination\\
20 & 16 & 14 & timetable\\
16 & 16 & 14 & tournament\\
36 & 36 & 14 & vlsat\\
\hline
1260 & 1012 & 300 & $\Sigma$
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{c||ccc|c}
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline\hline
new instances & 114 & 78 & 108 & 300 \\
old instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

With the introduction of IPASIR (Re-entrant Incremental Solver API), the incremental library track took place for the first time in SAT~Race~2015~\cite{Balyo:2015:SATRace}, and then again in SAT~Competitions 2016 and 2017. 
In SAT~Competitions 2020, we run the track again and selected a total $300$ benchmark instances for the six applications described below.

\paragraph{Backbone Detection}

The application $\mathsf{genipabones}$ reads a formula from a given file and transforms it using the dual rail encoding, i.e., it replaces each $x$ by $p_x$ and each $\overline{x}$ by $n_x$ and adds clauses of the form ($\overline{p_x} \vee \overline{n_x}$). 
Incrementally, each variable is then checked if it is a backbone variable or not. 
For this application, we selected $50$ of the smallest and easiest satisfiable problems of previous SAT competitions.

\paragraph{Essential Variables Calculation}

%Given a satisfiable formula $F$, a variable $x$ is essential for the satisfiability of $F$ if a truth value must be assigned to $x$ in each satisfying partial assignment of F. 
The application $\mathsf{genipaessentials}$ incrementally finds all the variables essential for the satisfiability of a given formula by testing each variable using the dual-rail encoded formula. 
For this application, we used the same easy satisfiable problems as in the Backbone Detection application.

\paragraph{Longest Simple Path Computation}

The application $\mathsf{genipalsp}$ finds the longest simple path in a graph. 
For this application, we selected $50$ instances of the smallest graphs provided by Balyo et al.~\cite{Balyo:2019:LSP}.

\paragraph{MaxSAT}

The application $\mathsf{genipamax}$ is a trivial partial MaxSAT solver based on adding activation literals to soft clauses and 
subsequent incremental optimization using a cardinality constraint~\cite{Philipp:2015:PBLib} and assumptions. 
For this application, we selected $50$ instances from MaxSAT Evaluation 2019\footnote{\url{https://maxsat-evaluations.github.io/2019/}}.

\paragraph{QBF}
$\mathsf{Ijtihad}$ is a solver for Quantified Boolean Formulas (QBFs). 
The solver tackles the a formula iteratively, using counterexample-guided expansion~\cite{Bloem:2018:QBFSAT}.
For this application, we selected $50$ instances from QBF Evaluation 2019\footnote{\url{http://www.qbflib.org/qbfeval19.php}}.

\paragraph{Planning}
$\mathsf{Pasar}$ is a planer which is based on the principles of counter-example guided abstraction refinement(CEGAR)~\cite{Froleyks:2019:Pasar}. 
For this application, we selected $50$ sas planning instances.

@@

\section{History of Code and Winning Strategies}
\label{sec:analysis}

In the following we provide an overview on the participating teams and solvers,  and summarize new strategies which are implemented in the award winning solvers of this competition.

We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
Our survey of the winning strategies in this competition starts with sequential (including incremental) SAT solving in Section~\ref{sec:part:seq}, then we continue with parallel SAT solving in Section~\ref{sec:part:par} and conclude with solvers in the cloud track in Section~\ref{sec:part:cloud}.

\subsection{On the Shoulders of Giants: The Evolution of SAT Solvers}
\label{sec:codebases}

With a few exceptions, progress in SAT solvers emerged as extensions or forks from existing code bases. 
One well-known tree of development is rooted in the Codebase of the Minisat solver by Niklas Éen and Niklas Sörenson~\cite{}. 
The most well-known fork of Minisat is the Glucose solver by Gilles Audemard and Laurent Simon~\cite{}.  
The authors of Glucose introduced numerous implementations of successful new methods, e.g., Literal Block Distance (LBD)~\cite{}, which they recently summarized in~\cite{}.

The SAT solver RISS by Norbert Manthey is a successful and award winning fork of Glucose (version 2.2) in combination with the state-of-the-art preprocessor Coprocessor~\cite{}.

Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh~\cite{}. 
Maple first emerged as a series of forks submitted to SAT Competition 2016, introducing the two new branching heuristics Learning Rate based Branching (LRB) and Conflict History based Branching (CHB)~\cite{}. 
The then award winning variant MapleCOMSPS is an implementation of the LRB heuristic on top of CoMinisatPS~\cite{}. 
The award winning derivatives of MapleCOMSPS in SAT Competition 2017 include a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}. 
Its extension MapleLCMDistChronoBT-DL with a new clause learning/forgetting heuristic Duplicate Learnts (DL)~\cite{} won SAT Race 2019. 
The success story of Maple resulted also in numerous submissions of modified Maple solvers in this competition, some of which have been successful (see Section~\ref{}).

CryptoMinisat by Mate Soos emerged as a fork of Minisat with an extension that brings special handling of xor clauses via gaussian elimination, which is especially effective when solving cryptographic instances~\cite{}. 
Today, CryptoMinisat is more of an independent code base than a Minisat fork coming with award winning individual implementations of recent SAT technology (see Section~\ref{}).

The SAT solvers of Armin Biere arguably belong to the best and most well-known independent code-bases. 
Lingeling has been around for years now and still we had competitive submissions of its parallel versions Plingeling in this competition. 
CaDiCal came up in SAT Competition 2017 and has been award winning since then. 
The reimplementation of CaDiCal in the new SAT solver Kissat set a new standard in sequential SAT solving in this competition (see Section~\ref{}).

\subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}
\label{sec:part:seq}

A total of $18$ teams submitted their solvers to the main track of the competition.  
Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
$14$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or Cadical~\cite{}.

In the incremental track, four teams submitted their solvers. 
All solvers in the incremental library track are created from independent code bases. 
Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers.

@@

\subsection{Parallel SAT Solving: Winners of the Parallel Track}
\label{sec:part:par}

@@

\subsection{Massively Parallel SAT Solving: Winners of the Cloud Track}
\label{sec:part:cloud}
